Beyond Ultra-Diffuse Galaxies I: Mass-Size Outliers Among the Satellites of Milky Way Analogs

### 2022-10-25 paper1.tex
just did a final read. But have to think more about the sky area used for background subtraction. Is it the area of 250 hosts, or 689 hosts?

\author[0000-0002-1841-2252]{Rachael Beaton}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\author[0000-0002-2991-9251]{Kirsten Casey}
\affiliation{Center for Cosmology and AstroParticle Physics (CCAPP), The Ohio State University, Columbus, OH 43210, USA}
\author[0000-0002-1841-2252]{Shany Danieli}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\author[0000-0002-1841-2252]{Andy Goulding}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\author[0000-0002-2704-5028]{Remy Joseph}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\affiliation{Oskar Klein Centre for Cosmoparticle Physics, Department of Physics, Stockholm University, Stockholm SE-106 91, Sweden}
\author[0000-0002-1841-2252]{Erin Kado-Fong}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}

@@

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
Large diffuse galaxies are hard to find, but understanding the environments where they live and their numbers, and ultimately their origins, is of intense interest and important for galaxy formation and evolution. Using Subaru's Hyper Suprime-Cam Strategic Survey Program, we perform a systematic search for low surface brightness galaxies and present novel and effective methods for detecting and modeling them. 
As a case study, we build a large sample of galaxies that are outliers in the mass-size relation and are satellites of Milky Way analogs in the nearby Universe ($0.01 < z < 0.04$). These ``ultra-puffy'' galaxies (UPGs), defined to be $1.5\sigma$ above the average mass-size relation, represents the tail of the satellite size distribution. We find that each MW analog hosts $N_{\rm UPG} = 0.61\pm 0.04$ ultra-puffy galaxies on average, which is slightly smaller than the observed abundance at this halo mass in the Local Volume. We also construct a sample of ultra-diffuse galaxies (UDGs) in MW analogs and find an abundance of $N_{\rm UDG} = 0.76\pm0.04$ per host. With literature results, we confirm that the UDG abundance scales with the host halo mass following a sublinear power law. We argue that our definition for ultra-puffy galaxies, which is based on the mass-size relation, is more physically-motivated than the common definition of ultra-diffuse galaxies, which depends on an arbitrary surface brightness cut and thus yields different surface mass density cuts for quenched and star-forming galaxies. 
\end{abstract}

@@

\section{Introduction} \label{sec:intro}
In a variety of galaxies in the Universe, there is an interesting subset of galaxies with low surface brightness \citep[dubbed low surface brightness galaxies or LSBGs, e.g.,][]{Sandage1984,Caldwell1987,Impey1988,McGaugh1995,Dalcanton1997a}. Recently, new excitement has been generated by the discovery of a large population of ultra-diffuse galaxies (UDGs) in the Coma cluster \citep{vanDokkum2015}, accompanied by many other works on detecting UDGs in clusters \citep[e.g.,][]{Koda2015,Mihos2015,Yagi2016,vdBurg2016,vdBurg2017,Lee2017,ManceraPina2018,Zaritsky2019}, groups \citep[e.g.,][]{Roman2017b,Greco2018,SAGA-II,CarlstenELVES2022}, and the field \citep[e.g.,][]{Leisman2017,Roman2019,Prole2019,Tanoglidis2021,Kadowaki2021}. There have been a variety of studies of these diffuse galaxy systems, ranging from their dark matter content \citep[e.g.,][]{Mowla2017,vanDokkum2018,vanDokkum2019,Wasserman2019,Keim2022}, to their globular cluster populations \citep[e.g.,][]{vanDokkum2017,Somalwar2020,Forbes2020,Danieli2022,Gannon2022,vanDokkum2022GC}, and their stellar populations \citep[e.g.,][]{Gu2018,Ferre-Mateu2018,Villaume2022}. UDGs are defined to be galaxies with large size ($r_e > 1.5$ kpc) and low surface brightness ($\sbcen > 24.0\ \sbunit$), and thus UDGs are outliers in size and surface brightness compared to normal dwarf galaxies. A central question about LSBGs, including UDGs, is what causes them to be outliers from the average mass-size relation of dwarf galaxies?

Various mechanisms have been proposed to explain the presence of large, diffuse galaxies (as mass-size outliers) across different environments. In the field (i.e, in isolation), their large sizes might be caused by stellar feedback \citep{DiCintio2017,Chan2018}, early galaxy mergers \citep{Wright2021}, passing into and out of a more massive halo (so-called backsplash satellites, \citealt{Benavides2021}), or by inhabiting halos with higher spin \citep{Dalcanton1997,Amorisco2016,Liao2019,Benavides2022}. In groups and clusters, their large sizes may ensue from tidal heating near pericenter \citep{Jiang2019}, via adiabatic expansion due to mass loss \citep{Tremmel2020}, or even via a bullet-dwarf collision \citep{vandokkum2022Nat,vanDokkum2022GC}. Despite theoretical advances, it is still an open question how mass-size outliers like UDGs are formed. It is also unclear whether mass-size outliers belong to a distinct class of galaxies or are just a natural extension of dwarf systems to lower surface brightness or larger size. A straightforward way to answer these questions is to compare mass-size outliers with ``normal'' low mass galaxies which have been studied extensively.

Our best understanding of the low mass galaxy regime comes from the satellite system of our Milky Way (MW) and the Local Group (LG) \citep[e.g.,][]{McConnachie2012,Simon2019}. With the advent of deep sky surveys and dedicated spectroscopic programs, we are now in a position to also map the satellite systems of MW analogs (typically defined as galaxies having similar stellar mass or halo mass to MW) in the Local Volume and nearby Universe. The Satellites Around Galactic Analogs survey (SAGA, \citealt{SAGA-I,SAGA-II}) is designed to spectroscopically confirm the satellites of 100 MW analogs at 20--40 Mpc. The Exploration of Local VolumE Satellites survey (ELVES,  \citealt{ELVES-I,ELVES-II,CarlstenELVES2022}) uses deep imaging data to identify satellite candidates of MW-like hosts in the Local Volume (LV, $D<12$ Mpc) and estimate surface brightness fluctuation distances from images to confirm their association with their hosts. Having these MW satellites as a reference frame, we can contrast them with the mass-size outliers in the same environment to understand the formation of large diffuse galaxies. However, there are only $\sim 40$ confirmed UDGs associated with MW analogs in the literature \citep{Roman2017b,Cohen2018,SAGA-II,CarlstenELVES2022,Nashimoto2022,Karunakaran2022b}. Therefore, a larger sample of mass-size outliers associated with MW-like hosts is needed to conduct such a comparison between the mass-size outliers and the normal satellites.

The goal of this paper is to find and study large diffuse satellite galaxies in the context of MW analogs. Leveraging the depth and wide sky coverage of Hyper-Suprime Cam (HSC) Subaru Strategic Program imaging data, we perform a search for LSBGs using novel methods in detection, false positive identification, and modeling. We further build a large sample of mass-size outliers that are likely satellites of MW-mass hosts in the nearby Universe. We propose a new definition for mass-size outliers, dubbed ``\textit{ultra-puffy galaxies}'' (UPGs), based on the observed mass-size relation in the Local Volume using ELVES sample. This concept is less affected by the galaxy color and provides a robust avenue to study the mass-size outlier population. 
We calculate the abundance of mass-size outliers in MW analogs and compare with their abundances in other environments. Our results seek to shed light on the role of environment on the formation of large diffuse dwarf galaxies. 
%By comparing mass-size outliers with normal satellites and simulations, our results seek to shed light on the formation and evolution of the large diffuse galaxies.

@@

The layout of this paper is as follows. Section \ref{sec:data} describes the data used in this work. In Section \ref{sec:lsbg_search}, we describe the LSBG search in HSC data, including source detection (\S \ref{sec:detection}), deblending (\S \ref{sec:deblending}), modeling (\S \ref{sec:modeling}), and completeness and uncertainty (\S\ref{sec:comp_meas}). In Section \ref{sec:sample_construction}, we propose a new definition for large and diffuse galaxies (the UPGs) and present our UDG and UPG samples. In Section \ref{sec:results}, we compare the UDGs and UPGs on the mass-size plane. We calculate their abundances and compare with literature (\S \ref{sec:n_udg}). Based on these results, we further argue why we need to move beyond UDG and adopt the UPG definition in Section \ref{sec:discussion}. Section \ref{sec:summary} presents a summary of this work and prospects for the future. In a companion paper (Li et al., to be submitted), we discuss the size distributions, spatial distributions, and quenching of UDGs and UPGs.

In this work, we refer to LSBGs as objects selected purely by surface brightness without knowing distance information. We refer to mass-size outliers (including UDGs and UPGs) as galaxies with large physical sizes compared to normal dwarf galaxies. We adopt a flat $\Lambda$CDM cosmology from \citet{Planck15} with $\Omega_{\rm m}= 0.307$ and $H_0 = 67.7\ $km s$^{-1}$ Mpc$^{-1}$. We use the AB system \citep{Oke1983} for magnitudes. The stellar mass used in this work is based on a \citet{Chabrier2003} initial mass function.

\section{Data} \label{sec:data}
\subsection{Hyper Suprime-Cam Subaru Strategic Program}
The Hyper Suprime-Cam Subaru Strategic Program (HSC-SSP, \citealt{Aihara2018}; hereafter the HSC survey)\footnote{\url{https://hsc-release.mtk.nao.ac.jp/doc/}} is an optical imaging survey using the 8.2-m Subaru telescope and the Hyper Suprime-Camera \citep{Miyazaki2012, Miyazaki2018}. The \texttt{Wide} layer is designed to cover $\sim 1000\ \rm{deg}^{2}$ of the sky in five broad bands ($grizy$), reaching a depth of $g=26.6$ mag, $r=26.2$ mag and $i=26.2$ mag ($5\sigma$ point source detection). HSC data are processed using the \code{hscPipe}\footnote{\url{https://hsc.mtk.nao.ac.jp/pipedoc_e/}} \citep{Bosch2018}, which is a customized version of the Vera Rubin Observatory Legacy Survey of Space and Time (LSST) pipeline \citep{LSST-pipeline}\footnote{\url{https://pipelines.lsst.io/}}.

@@

\subsection{NASA-Sloan Atlas}
We use the NASA-Sloan Atlas (NSA\footnote{\url{http://nsatlas.org}}, \citealt{Blanton2005,Blanton2011}) to select galaxies that are analogous to our Milky Way based on their stellar mass (see \S\ref{sec:match}), then we match the LSBGs to these MW analogs. The NSA catalog provides various physical properties of galaxies in the nearby Universe as derived from the Sloan Digital Sky Survey \citep[SDSS,][]{York2000}. We use the most recent version of the NSA catalog (\code{v1\_0\_1}\footnote{\url{https://www.sdss.org/dr13/manga/manga-target-selection/nsa/}}) which contains about $640,000$ galaxies out to $z < 0.15$. This version also updates the aperture photometry to elliptical Petrosian photometry since it is considered to be more reliable than the photometry used in the older versions. In this paper, we use the stellar masses derived from the elliptical Petrosian photometry using \code{kcorrect v4\_2} \citep{Blanton2007}. The redshifts of the galaxies in NSA come from several spectroscopic surveys, \ion{H}{1} gas surveys, or direct distance measurements.

@@

Continuing the work of \citet{Greco2018} (hereafter \citetalias{Greco2018}), we conduct a systematic search for low surface brightness galaxies (LSBGs) in the HSC PDR2 data, which covers $\sim 1.5$ times the sky area of \citetalias{Greco2018}. The schematic of the searching method in this paper remains similar to that in \citetalias{Greco2018}, but we do improve the search completeness and purity by adding several new steps, which are highlighted in this section. We outline the major steps below and refer the reader who are already familiar with the algorithms in LSBG searches to \S \ref{sec:sample_construction} for the UDG and UPG sample construction.

\begin{enumerate}
    \item Source Detection (\S \ref{sec:detection}): we run \href{https://www.astromatic.net/software/sextractor/}{\code{SourceExtractor}} \citep{Bertin1996} on the coadd images after removing bright extended sources. Then we apply an initial size and color cut based on the output catalog. 
    \item Deblending (\S \ref{sec:deblending}): we remove false positives that are not likely to be LSBGs by running \href{https://pmelchior.github.io/scarlet/}{\code{scarlet}} \citep{Melchior2018}. We use the \code{scarlet} models to define color-size-morphology-surface brightness cuts. This step removes roughly 97\% of false positives.
    \item Modeling (\S \ref{sec:modeling}): we fit a parametric model to the LSBGs to estimate their structural parameters. 
    \item Completeness and measurement uncertainties (\S \ref{sec:comp_meas}) are characterized by injecting mock \sersic{} galaxies into images. 
\end{enumerate}
The number of objects remaining after each step is shown in Table \ref{tab:steps_flow}. Our source detection pipeline \code{hugs}\footnote{\url{https://github.com/johnnygreco/hugs}} and the deblending and modeling code \code{kuaizi}\footnote{\url{https://github.com/AstroJacobLi/kuaizi}} are open-sourced and available online.

@@

\subsection{Source Detection}\label{sec:detection}
\citetalias{Greco2018} performed a search for LSBGs in the first $\sim 200$ deg$^2$ of the HSC survey and uncovered 781 LSBGs. We continue the work in \citetalias{Greco2018} and extend the search to the HSC PDR2 data, which covers $\sim 300\ \rm{deg}^{2}$ and has a sky subtraction better suited for LSB studies compared to previous data releases. We follow the same method for source detection as in \citetalias{Greco2018}, but make several updates to accommodate the PDR2 data. These updates are guided by both our understanding of PDR2 data and completeness tests using mock galaxies. We summarize the main steps of the LSBG search method here, and refer the interested reader to \citetalias{Greco2018} and Appendix \ref{ap:detection} for more details. 
% In the following, we summarize the main steps of the search and emphasize the updates made to improve the overall completeness and purity. We refer the interested readers to \citetalias{Greco2018} for more details.

We start by replacing the bright sources and their associated LSB outskirts with the sky noise. Bright objects and their diffuse light are identified using surface brightness thresholding. Then we run a detection using \href{https://sep.readthedocs.io/en/v1.1.x}{\code{sep}} \citep{Barbary2016} to remove small compact sources and noisy peaks and replace their footprints with sky noise. We use \code{SourceExtractor} to detect sources on the ``cleaned'' images with a low detection threshold. Taking the output catalog from \code{SourceExtractor}, we apply an initial selection based on the size, color, and peakiness of objects.

After these steps, we have an initial sample that contains 86,002 LSBG candidates. We obtain four times more sources per square degree ($\sim 280\ \mathrm{deg}^{-2}$) than \citetalias{Greco2018} mainly because HSC PDR2 has a sky subtraction suited for finding LSB features, our detection here is more inclusive of larger objects, and our size cut is less restrictive for small objects. Among these objects, there are still a lot of false positives, including shredded galaxy outskirts, tidal features, Galactic cirrus, and blended compact sources. Therefore, we perform an extra ``deblending'' step to further remove false positives.

% {\bf Here you put one PP summarizing the main changes, and then put the rest of the details in 3.1 into Appendix 1. End this section with the numbers of targets at the end of this step, and I agree with Erin that having a flow-table with the numbers per step would be nice.}

@@

\begin{figure*}
	\vbox{ 
		%\vskip -10mm
		\centering
		\includegraphics[width=1\linewidth]{vanilla_scarlet_demo.pdf}
		\includegraphics[width=1\linewidth]{vanilla_scarlet_demo2.pdf}
	}
	\caption{A demonstration of the deblending step as described in \S\ref{sec:deblending} and \S\ref{ap:deblending}. Here we show two objects from our initial sample: the one shown in the top panels is a blue LSBG, whereas the one shown in the bottom is a false positive detection which is a blend between high-$z$ galaxy and galaxy outskirts. The first columns show the $griz$ color-composite images with the bounding boxes overlaid. The objects covered by the gray shades are masked during fitting. The remaining columns show the initial model, the optimized model (PSF convolved), the residual image, and the optimized model of the target galaxy only. 
	}
	\label{fig:vanilla_scarlet_demo}
\end{figure*}

Removing false positives from the initial sample while retaining high completeness is one of the major challenges in LSBG searches \citep[e.g.,][]{vanDokkum2015,Koda2015,Yagi2016,Greco2018,SAGA-I,Zaritsky2019,Zaritsky2021,Tanoglidis2021,Zaritsky2022}. A common type of false positive occurs when point-like sources are blended with diffuse light from background galaxies or the LSB outskirts of stars and galaxies. Our initial detection cannot distinguish them from real LSBGs. In order to identify and remove these objects from our sample, we perform non-parametric modeling using \href{https://pmelchior.github.io/scarlet/}{\code{scarlet}} \citep{Melchior2018} and design an efficient metric to remove false positives.

\subsubsection{\code{Scarlet} fitting}
\code{Scarlet} is a deblending and modeling tool designed for multi-band and multi-resolution imaging data. It utilizes color and morphology information to separate blended objects. In the following, we briefly summarize how \code{scarlet} works, and we refer the interested readers to \citet{Melchior2018,Melchior2021} and the online documentation\footnote{\url{https://pmelchior.github.io/scarlet/}} for more details.

>>>>

\author[0000-0002-1841-2252]{Rachael Beaton}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\author[0000-0002-2991-9251]{Kirsten Casey}
\affiliation{Center for Cosmology and AstroParticle Physics (CCAPP), The Ohio State University, Columbus, OH 43210, USA}
\author[0000-0002-1841-2252]{Shany Danieli}
\altaffiliation{NASA Hubble Fellow}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\author[0000-0002-1841-2252]{Andy Goulding}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\author[0000-0002-2704-5028]{Remy Joseph}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\affiliation{Oskar Klein Centre for Cosmoparticle Physics, Department of Physics, Stockholm University, Stockholm SE-106 91, Sweden}
\author[0000-0002-1841-2252]{Erin Kado-Fong}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}

@@

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
Large diffuse galaxies are hard to find, but understanding the environments where they live, their numbers, and ultimately their origins, is of intense interest and importance for galaxy formation and evolution. Using Subaru's Hyper Suprime-Cam Strategic Survey Program, we perform a systematic search for low surface brightness galaxies and present novel and effective methods for detecting and modeling them. 
As a case study, we build a large sample of galaxies that are outliers in the mass-size relation and are satellites of Milky Way analogs in the nearby Universe ($0.01 < z < 0.04$). These ``ultra-puffy'' galaxies (UPGs), defined to be $1.5\sigma$ above the average mass-size relation, represent the tail of the satellite size distribution. We find that each MW analog hosts $N_{\rm UPG} = 0.61\pm 0.04$ ultra-puffy galaxies on average, which is consistent with the observed abundance at this halo mass in the Local Volume. We also construct a sample of ultra-diffuse galaxies (UDGs) in MW analogs and find an abundance of $N_{\rm UDG} = 0.76\pm0.04$ per host. With literature results, we confirm that the UDG abundance scales with the host halo mass following a sublinear power law. We argue that our definition for ultra-puffy galaxies, which is based on the mass-size relation, is more physically-motivated than the common definition of ultra-diffuse galaxies, which depends on surface brightness and size cuts and thus yields different surface mass density cuts for quenched and star-forming galaxies. 
\end{abstract}

@@

\section{Introduction} \label{sec:intro}
In a variety of galaxies in the Universe, there is an interesting subset of galaxies with low surface brightness \citep[dubbed low surface brightness galaxies or LSBGs, e.g.,][]{Sandage1984,Caldwell1987,Impey1988,McGaugh1995,Dalcanton1997a}. Recently, new excitement has been generated by the discovery of a large population of ultra-diffuse galaxies (UDGs) in the Coma cluster \citep{vanDokkum2015}, accompanied by many other works on detecting UDGs in clusters \citep[e.g.,][]{Koda2015,Mihos2015,Yagi2016,vdBurg2016,vdBurg2017,Lee2017,ManceraPina2018,Zaritsky2019,Danieli2019}, groups \citep[e.g.,][]{Roman2017b,Greco2018,SAGA-II,CarlstenELVES2022}, and the field \citep[e.g.,][]{Leisman2017,Roman2019,Prole2019,Tanoglidis2021,Kadowaki2021}. There have been a variety of studies of these diffuse galaxy systems, ranging from their dark matter content \citep[e.g.,][]{Mowla2017,vanDokkum2018,vanDokkum2019,Danieli2019DF2,Wasserman2019,Keim2022}, to their globular cluster populations \citep[e.g.,][]{vanDokkum2017,Somalwar2020,Forbes2020,Danieli2022,Gannon2022,vanDokkum2022GC}, and their stellar populations \citep[e.g.,][]{Gu2018,Ferre-Mateu2018,Pandya2018,Villaume2022}. We refer to LSBGs as objects selected purely by surface brightness without distance information. When knowing distances, people define UDGs to be galaxies with large sizes ($r_e > 1.5$ kpc) and low surface brightnesses ($\sbcen > 24.0\ \sbunit$), and thus UDGs are outliers in size and surface brightness compared to normal dwarf galaxies. A central question about LSBGs, including UDGs, is what causes them to be outliers from the average mass-size relation of dwarf galaxies.

Various mechanisms have been proposed to explain the presence of large, diffuse galaxies (as mass-size outliers) across different environments. In the field (i.e, in isolation), their large sizes might be a result of stellar feedback \citep{DiCintio2017,Chan2018}, early galaxy mergers \citep{Wright2021}, passing into and out of a more massive halo (so-called backsplash satellites; \citealt{Benavides2021}), or by inhabiting halos with higher spin \citep{Dalcanton1997,Amorisco2016,Liao2019,Benavides2022}. In groups and clusters, their large sizes may ensue from tidal heating near pericenter \citep{Jiang2019}, via adiabatic expansion due to mass loss \citep{Tremmel2020}, or even via a bullet-dwarf collision \citep{vandokkum2022Nat,vanDokkum2022GC}. Despite theoretical advances, it is still an open question how mass-size outliers like UDGs are formed. It is also unclear whether mass-size outliers belong to a distinct class of galaxies or are just a natural extension of dwarf systems to lower surface brightness or larger size. A straightforward way to answer these questions is to compare mass-size outliers with ``normal'' low mass galaxies which have been studied extensively.

Our best understanding of the low mass galaxy regime comes from the satellite system of our Milky Way (MW) and the Local Group (LG) \citep[e.g.,][]{McConnachie2012,Simon2019}. With the advent of deep sky surveys and dedicated spectroscopic programs, we are now in a position to also map the satellite systems of MW analogs (typically defined as galaxies having similar stellar mass or halo mass to MW) in the Local Volume and nearby Universe. The Satellites Around Galactic Analogs survey (SAGA, \citealt{SAGA-I,SAGA-II}) is designed to spectroscopically confirm the satellites of 100 MW analogs at 20--40 Mpc. The Exploration of Local VolumE Satellites survey (ELVES,  \citealt{ELVES-I,ELVES-II,CarlstenELVES2022}) uses deep imaging data to identify satellite candidates of MW-like hosts in the Local Volume (LV, $D<12$ Mpc) and estimate surface brightness fluctuation distances from images to confirm their association with their hosts. Having these satellites of MW analogs as a reference frame, we can contrast them with the mass-size outliers in the same environment to understand the formation of large diffuse galaxies. However, there are only $\sim 40$ confirmed UDGs associated with MW analogs in the literature \citep{Roman2017b,Cohen2018,SAGA-II,CarlstenELVES2022,Nashimoto2022,Karunakaran2022b}. Therefore, a larger sample of mass-size outliers associated with MW-like hosts is needed to conduct such a comparison between the mass-size outliers and the normal satellites.

The goal of this paper is to find and study large diffuse satellite galaxies in the context of MW analogs. Leveraging the depth and wide sky coverage of Hyper-Suprime Cam (HSC) Subaru Strategic Program imaging data, we perform a search for LSBGs using novel methods in detection, false positive identification, and modeling. We further build a large sample of mass-size outliers that are likely satellites of MW-mass hosts in the nearby Universe. We propose a new definition for mass-size outliers, dubbed ``\textit{ultra-puffy galaxies}'' (UPGs), based on the observed mass-size relation in the Local Volume using the ELVES sample. This concept is less affected by the galaxy color and provides a robust avenue to study the mass-size outlier population. 
We calculate the abundance of mass-size outliers in MW analogs and compare with their abundances in other environments. Our results seek to shed light on the role of environment on the formation of large diffuse dwarf galaxies. 
%By comparing mass-size outliers with normal satellites and simulations, our results seek to shed light on the formation and evolution of the large diffuse galaxies.

@@

The layout of this paper is as follows. Section \ref{sec:data} describes the data used in this work. In Section \ref{sec:lsbg_search}, we describe the LSBG search in HSC data, including source detection (\S \ref{sec:detection}), deblending (\S \ref{sec:deblending}), modeling (\S \ref{sec:modeling}), completeness, and uncertainty (\S\ref{sec:comp_meas}). In Section \ref{sec:sample_construction}, we propose a new definition for large and diffuse galaxies (the UPGs) and present our UDG and UPG samples. In Section \ref{sec:results}, we compare the UDGs and UPGs on the mass-size plane. We calculate their abundances and compare with the literature (\S \ref{sec:n_udg}). Based on these results, we further argue that we should move beyond UDGs and adopt the UPG definition in Section \ref{sec:discussion}. Section \ref{sec:summary} presents a summary of this work and prospects for the future. In a companion paper (Li et al., to be submitted), we discuss the size distributions, spatial distributions, and quenching of UDGs and UPGs.

In this work, we refer to mass-size outliers (including both UDGs and UPGs) as galaxies with large physical sizes compared to normal dwarf galaxies. We adopt a flat $\Lambda$CDM cosmology from \citet{Planck15} with $\Omega_{\rm m}= 0.307$ and $H_0 = 67.7\ $km s$^{-1}$ Mpc$^{-1}$. We use the AB system \citep{Oke1983} for magnitudes. The stellar mass used in this work is based on a \citet{Chabrier2003} initial mass function.

\section{Data} \label{sec:data}
\subsection{The Hyper Suprime-Cam Subaru Strategic Program}
The Hyper Suprime-Cam Subaru Strategic Program (HSC-SSP, \citealt{Aihara2018}; hereafter the HSC survey)\footnote{\url{https://hsc-release.mtk.nao.ac.jp/doc/}} is an optical imaging survey using the 8.2-m Subaru telescope and the Hyper Suprime-Camera \citep{Miyazaki2012, Miyazaki2018}. The \texttt{Wide} layer is designed to cover $\sim 1000\ \rm{deg}^{2}$ of the sky in five broad bands ($grizy$), reaching a depth of $g=26.6$ mag, $r=26.2$ mag and $i=26.2$ mag ($5\sigma$ point source detection). HSC data are processed using  \code{hscPipe}\footnote{\url{https://hsc.mtk.nao.ac.jp/pipedoc_e/}} \citep{Bosch2018}, which is a customized version of the Vera Rubin Observatory Legacy Survey of Space and Time (LSST) pipeline \citep{LSST-pipeline}\footnote{\url{https://pipelines.lsst.io/}}.

@@

\subsection{NASA-Sloan Atlas}
We use the NASA-Sloan Atlas (NSA\footnote{\url{http://nsatlas.org}}, \citealt{Blanton2005,Blanton2011}) to select galaxies that are analogous to our Milky Way based on their stellar mass (see \S\ref{sec:match}), then we match the LSBGs to these MW analogs. The NSA catalog provides various physical properties of galaxies in the nearby Universe as derived from the Sloan Digital Sky Survey \citep[SDSS,][]{York2000}. We use the most recent version of the NSA catalog (\code{v1\_0\_1}\footnote{\url{https://www.sdss.org/dr13/manga/manga-target-selection/nsa/}}) which contains about $640,000$ galaxies out to $z < 0.15$. This version also updates the aperture photometry to elliptical Petrosian photometry which is considered to be more reliable than the photometry used in the older versions. In this paper, we use the stellar masses derived from the elliptical Petrosian photometry using \code{kcorrect v4\_2} \citep{Blanton2007}. The redshifts of the galaxies in the NSA come from several spectroscopic surveys, \ion{H}{1} gas surveys, or direct distance measurements.

@@

Continuing the work of \citet{Greco2018} (hereafter \citetalias{Greco2018}), we conduct a systematic search for low surface brightness galaxies in the HSC PDR2 data, which covers $\sim 1.5$ times the sky area of \citetalias{Greco2018}. The schematic of the searching method in this paper remains similar to that in \citetalias{Greco2018}, but we do improve the search completeness and purity by adding several new steps, which are highlighted in this section. We outline the major steps below and refer the reader who are already familiar with the algorithms in LSBG searches to \S \ref{sec:sample_construction} for the mass-size outlier sample construction.

\begin{enumerate}
    \item Source Detection (\S \ref{sec:detection}): we run \href{https://www.astromatic.net/software/sextractor/}{\code{SourceExtractor}} \citep{Bertin1996} on the coadd images after removing bright extended sources. Then we apply an initial size and color cut based on the output catalog. 
    \item Deblending (\S \ref{sec:deblending}): we remove false positives that are not likely to be LSBGs by running \href{https://pmelchior.github.io/scarlet/}{\code{scarlet}} \citep{Melchior2018}. We use the \code{scarlet} models to define color-size-morphology-surface brightness cuts. This step removes roughly 98\% of false positives.
    \item Modeling (\S \ref{sec:modeling}): we fit a parametric model to the LSBGs to estimate their properties including size, total magnitude, and average surface brightness. 
    \item Completeness and measurement bias and uncertainties (\S \ref{sec:comp_meas}) are characterized by injecting mock \sersic{} galaxies into images and recovering them following the procedures as described above. 
\end{enumerate}
The number of objects remaining after each step is shown in Table \ref{tab:steps_flow}. Our source detection pipeline \code{hugs}\footnote{\url{https://github.com/johnnygreco/hugs}} and the deblending and modeling code \code{kuaizi}\footnote{\url{https://github.com/AstroJacobLi/kuaizi}} are open-sourced and available online.

@@

\subsection{Source Detection}\label{sec:detection}
\citetalias{Greco2018} performed a search for LSBGs in the first $\sim 200$ deg$^2$ of the HSC survey and uncovered 781 LSBGs. We continue the work in \citetalias{Greco2018} and extend the search to the HSC PDR2 data, which covers $\sim 300\ \rm{deg}^{2}$ and has a sky subtraction better suited for LSB studies compared to prior data releases. We follow the same method for source detection as in \citetalias{Greco2018}, but make several updates to accommodate the PDR2 data. These updates are guided by both our understanding of PDR2 data and completeness tests using mock galaxies. We summarize the main steps of the LSBG search method here, and refer the interested reader to \citetalias{Greco2018} and Appendix \ref{ap:detection} for more details. 
% In the following, we summarize the main steps of the search and emphasize the updates made to improve the overall completeness and purity. We refer the interested readers to \citetalias{Greco2018} for more details.

We start by replacing the bright sources and their associated LSB outskirts with the sky noise. Bright objects and their diffuse light are identified using surface brightness thresholding. We run an additional detection using \href{https://sep.readthedocs.io/en/v1.1.x}{\code{sep}} \citep{Barbary2016} to remove small compact sources and noisy peaks and replace their footprints with sky noise. Then we use \code{SourceExtractor} to detect sources on the ``cleaned'' images with a low detection threshold. Taking the output catalog from \code{SourceExtractor}, we apply an initial selection based on the size, color, and peakiness of objects.

After these steps, we have an initial sample that contains 86,002 LSBG candidates. We obtain four times more sources per square degree ($\sim 280\ \mathrm{deg}^{-2}$) than \citetalias{Greco2018} mainly because HSC PDR2 has a sky subtraction suited for finding LSB features, our detection here is more inclusive of larger objects, and our size cut is less restrictive for small objects. Among these objects, there are still many false positives, including shredded galaxy outskirts, tidal features, Galactic cirrus, and blended compact sources. Therefore, we perform an extra ``deblending'' step to further remove false positives.

@@

\begin{figure*}
	\vbox{ 
		%\vskip -10mm
		\centering
		\includegraphics[width=1\linewidth]{vanilla_scarlet_demo.pdf}
		\includegraphics[width=1\linewidth]{vanilla_scarlet_demo2.pdf}
	}
	\caption{A demonstration of the deblending step as described in \S\ref{sec:deblending} and \S\ref{ap:deblending}. Here we show two objects from our initial sample: the one shown in the top panels is a blue LSBG, whereas the one shown in the bottom is a false positive detection, which is a blend between high-$z$ galaxy and galaxy outskirts. The first columns show the $griz$ color-composite images with the bounding boxes overlaid. The objects covered by the gray shades are masked during fitting. The remaining columns show the initial model, the optimized model (PSF convolved), the residual image, and the optimized model of the target galaxy only. The red dashed circle in the rightmost column denotes the measured half-light radius.
	}
	\label{fig:vanilla_scarlet_demo}
\end{figure*}

Removing false positives from the initial sample while retaining high completeness is one of the major challenges in LSBG searches \citep[e.g.,][]{vanDokkum2015,Koda2015,Yagi2016,Greco2018,SAGA-I,Zaritsky2019,Zaritsky2021,Tanoglidis2021,Zaritsky2022}. A common type of false positive occurs when point-like sources are blended with diffuse light from background galaxies or the LSB outskirts of stars and galaxies. Our initial detection cannot distinguish them from real LSBGs. In order to identify and remove these objects from our sample, we perform non-parametric modeling of all LSBG candidates using \href{https://pmelchior.github.io/scarlet/}{\code{scarlet}} \citep{Melchior2018} and design an effective metric to remove false positives.

\subsubsection{\code{Scarlet} fitting}
\code{Scarlet} is a deblending and modeling tool designed for multi-band and multi-resolution imaging data. It utilizes color and morphology information to separate blended objects and model objects in a non-parametric fashion. In the following, we briefly summarize how \code{scarlet} works, and we refer the interested readers to \citet{Melchior2018,Melchior2021} and the online documentation\footnote{\url{https://pmelchior.github.io/scarlet/}} for more details.

In \code{scarlet}, each source $k$ in the cutout is described by a morphology image $S_k$ and a Spectral Energy Distribution (SED) vector $A_k$. The multi-band images are represented as $Y$. The goal of the modeling is to minimize the objective function $f = \frac{1}{2} ||Y - P \ast (\sum_k A_k^\top \times S_k)||^{2}$ under certain constraints, where $P$ is the PSF and $*$ is convolution. The morphology image of each source is limited by a bounding box. We assume two constraints when running \code{scarlet}: all sources have positive fluxes (positivity constraint) and the light profiles of all sources monotonically decrease from center to outskirts (monotonicity constraint). The monotonicity constraint is over-simplified for well-resolved galaxies with complicated structures, but for objects in our sample this assumption still holds for most cases and provides an effective and robust way to deblend overlapping sources. We refer to this modeling method as \textit{vanilla \code{scarlet}}.
